\documentclass{res}

\usepackage{multirow}
\textwidth=5.2in
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\name{Bram van der Kroef\\[12pt]}
\address{125 Third St. E\\Fort Frances, ON\\P9A 1P6\\
  bram@vanderkroef.net\\http://www.vanderkroef.net\\github.com/BramvdKroef}

\begin{resume}

\section{Summary}
\label{sec:summary}
 4 years of experience with PHP, Python, Java, Javascript, CSS, HTML,
 jQuery, MySQL Database administration, developing modules and themes
 for Drupal.

\section{Education}
\label{sec:edu}
B.S. of Information and Communication Technology, Hogeschool van
Amsterdam, Netherlands \\
Minor in Game Technology \\
September 2003 to July 2007

Programming in Java and C/C++, system and network engineering,
embedded systems, software engineering, artificial intelligence,
project management and communication skills.
  
\section{Experience}
\label{sec:experience}

{\bf Programmer,} Fort Frances Times Ltd. -- April 1, 2008 to present
\begin{itemize} \itemsep -2pt
\item Developing custom Drupal modules and themes for client
  websites. Maintenance on websites using HTML, PHP, Javascript,
  jQuery, CSS, MySQL and Drupal.
  \item Reduced time to install and configure a Drupal site (+
    modules) from half hour to minutes by using Python to automate the
    process. Create Drupal themes in half the time it took
    before. Automated launching of a website from development to live
    server with Python and shell scripts.
  \item Developing in-house software for keeping track of client
    information, project progress and billing in a MySQL database.
  \item Writing PHP software for the newspaper to manage subscriptions
    and paper routes in a MySQL database.
  \item Writing the software used in fishing tournaments for displaying
    team ranks and weight of fish. Software is used at the Fort Frances
    Canadian Bass Championship and the Emo Walleye Tournament.

    PHP software on a webserver manages tournament data in a MySQL
    database. Weights are entered through a web interface. Display
    screens are transferred to client PC's with ajax; info about the
    team on stage to the overhead projectors, notes to the MC on a
    screen on stage, and a leader board to a large TV screen. The
    screens are controlled with a JavaScript interface backstage.
\end{itemize}

{\bf Programmer,} Celsius Benelux B.V. -- July 1, 2007 to August 30, 2007
\begin{itemize} \itemsep -2pt
\item The company installs building control systems that control
  lighting, air conditioning, etc, in large buildings.

  The Java tool I created lets engineers set up lighting controls in
  buildings. The interface features blueprints of the floors on which
  icons can be placed that correspond to lights. The icons can be
  linked to sensors to turn them on and off and can be assigned to
  groups to control multiple lights in a room as one.

  The interface connects directly with the Java software on the
  control system so changes take effect immediately.
\end{itemize}

{\bf Intern,} Celsius Benelux B.V. -- February 5, 2007 to June 22, 2007
\begin{itemize} \itemsep -2pt
\item Created a Java application that generates manuals for
  custom building control systems. The tool queries the control system
  for equipment it controls and downloads documentation from the
  company's internal wiki. The documentation for all the equipment is
  assembled and a manual is generated in HTML, RTF (can be read in MS
  Word) and LateX.
\end{itemize}

{\bf Intern,} Open Sesame ICT -- September 1, 2005 to January 20, 2006
\begin{itemize} \itemsep -2pt
\item Programmed in PHP, Javascript and Python.
\item Developed features for the company's web based Content Management
  System and Document Management System products including: \\
  A module that converts MS Visio documents to web pages. \\
  A module that checks MySQL databases for corrupt tables. \\
  Drag \& drop for the web-based file manager. \\
  A module that checks an email account for new emails using IMAP
  and adds attachments to the Document Management System.
\end{itemize}

\section{Skills}
\label{sec:skills}

\begin{tabular}{l l}
Programming Languages: & Java, C/C++, Python, PHP, Javascript.\\
Areas: & Networks, Operating Systems, AI.\\
Operating Systems: & Linux, Windows, OSX.\\
Other: & Apache, MySQL, Drupal, CodeIgniter, CakePHP, jQuery, Emacs, Eclipse.\\
\end{tabular}

\end{resume}
\end{document}
