%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}

% Configure page margins with geometry
% \geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
\name{Bram}{van der Kroef}
\position{Software Engineer}
\address{125 Third St. E Fort Frances, ON P9A 1P6}

\mobile{(807)-276-7960} 
\email{bram@vanderkroef.net}
\homepage{www.vanderkroef.net}
\github{BramvdKroef}
\linkedin{bramvanderkroef}
% \stackoverflow{SOid}{SOname}
% \twitter{@twit}
% \skype{skypeid}
% \extrainfo{extra informations}

%\quote{``Make the change that you want to see in the world."}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Bram van der Kroef~~~·~~~Résumé}
  {\thepage}


  \cvsection{Skills}

  \cvparagraph
  Programming Languages: Java, C/C++, PHP, Python, Javascript.\\
  Areas: Networks, Operating Systems, AI.\\
  Operating Systems: Linux, Windows, OSX.\\
  Other: Apache, MySQL, Drupal, jQuery, Git, Emacs, Eclipse.\\

  \cvsection{Education}


  %-------------------------------------------------------------------------------
  %	CONTENT
  %-------------------------------------------------------------------------------
  \begin{cventries}

    %---------------------------------------------------------
    \cventry
        {B.S. of Information and Communication Technology} % Degree
        {Hogeschool van Amsterdam} % Institution
        {Netherlands} % Location
        {September 2003 to July 2007} % Date(s)
        {
          \begin{cvitems} % Description(s) bullet points
          \item {Programming in Java and C/C++, system and network engineering,
            embedded systems, software engineering, artificial intelligence,
            project management and communication skills.}
          \end{cvitems}
        }

        %---------------------------------------------------------
  \end{cventries}


  \cvsection{Experience}


  %-------------------------------------------------------------------------------
  %	CONTENT
  %-------------------------------------------------------------------------------
  \begin{cventries}

    %---------------------------------------------------------
    \cventry
        {Programmer} % Job title
        {Times Web Design} % Organization
        {Fort Frances, ON} % Location
        {April 1, 2008 to present} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Developing custom Drupal modules and themes for client websites. Maintenance on websites using HTML, PHP, Javascript, jQuery, CSS, MySQL and Drupal.}
          \item {Reduced time to install and configure a Drupal site (+ 
            modules) from half hour to minutes by using Python to automate the 
            process. Create Drupal themes in half the time it took 
            before. Automated launching of a website from development to live 
            server with Python and shell scripts.}
          \item {Developing in-house software for keeping track of client
            information, project progress and billing in a MySQL database.}
          \item {Writing PHP software for the newspaper to manage subscriptions
            and paper routes in a MySQL database.}
          \item {Writing the software used in fishing tournaments for displaying
            team ranks and weight of fish. Software is used at the Fort Frances
            Canadian Bass Championship and the Emo Walleye Tournament.
            PHP software on a webserver manages tournament data in a MySQL
            database. Weights are entered through a web interface. Display
            screens are transferred to client PC's with ajax; info about the
            team on stage to the overhead projectors, notes to the MC on a
            screen on stage, and a leader board to a large TV screen. The
            screens are controlled with a JavaScript interface backstage.}
          \end{cvitems}
        }

        %---------------------------------------------------------
        \cventry
            {Programmer} % Job title
            {Celsius Benelux B.V.} % Organization
            {Amersfoort, NL} % Location
            {July 1, 2007 to August 30, 2007} % Date(s)
            {
              \begin{cvitems} % Description(s) of tasks/responsibilities
              \item {The company installs building control systems that control
                lighting, air conditioning, etc, in large buildings.
                The Java tool I created lets engineers set up lighting controls in
                buildings. The interface features blueprints of the floors on which
                icons can be placed that correspond to lights. The icons can be
                linked to sensors to turn them on and off and can be assigned to
                groups to control multiple lights in a room as one.
                The interface connects directly with the Java software on the
                control system so changes take effect immediately.}
              \end{cvitems}
            }

            %---------------------------------------------------------
            \cventry
                {Intern} % Job title
                {Celsius Benelux B.V.} % Organization
                {Amersfoort, NL} % Location
                {February 5, 2007 to June 22, 2007} % Date(s)
                {
                  \begin{cvitems} % Description(s) of tasks/responsibilities
                  \item {Created a Java application that generates manuals for
                    custom building control systems. The tool queries the control system
                    for equipment it controls and downloads documentation from the
                    company's internal wiki. The documentation for all the equipment is
                    assembled and a manual is generated in HTML, RTF (can be read in MS
                    Word) and LateX.}
                  \end{cvitems} 
                }

                %---------------------------------------------------------
                \cventry
                    {Intern} % Job title
                    {Open Sesame ICT} % Organization
                    {NL} % Location
                    {September 1, 2005 to January 20, 2006} % Date(s)
                    {
                      \begin{cvitems} % Description(s) of tasks/responsibilities
                      \item {Programmed in PHP, Javascript and Python.}
                      \item {Developed features for the company's web based Content Management
                        System and Document Management System products including: \\
                        A module that converts MS Visio documents to web pages. \\
                        A module that checks MySQL databases for corrupt tables. \\
                        Drag \& drop for the web-based file manager. \\
                        A module that checks an email account for new emails using IMAP
                        and adds attachments to the Document Management System.}
                      \end{cvitems}
                    }

                    %---------------------------------------------------------
  \end{cventries}


%-------------------------------------------------------------------------------
\end{document}
